---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab06)
```

## Brute Force Implementation

Implementation of Knapsack algo using brute force brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel=FALSE)

    brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel=FALSE)

### Time Taken:

Using (parallel= FALSE): 0.016

Using (parallel= TRUE): 0.008

Command used:

    system.time (brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500, parallel=FALSE))

Tested on Linux, using 8/2 = 4 cores. Machine had 8 cores in total.

### How much time does it takes to run the algorithm for n = 16 objects?

Using (parallel= FALSE): 0.268

Using (parallel= TRUE): 0.019

### What performance gain could you get by parallelizing brute force search?

Almost 2x increase in speed: (0.016/0.08 = 2), for n=12

## Greedy Heuristic Implementation

### How much time does it takes to run the algorithm for n = 1000000 objects?

Time Taken: 0.783 s


## Dynamic Implementation

### How much time does it takes to run the algorithm for n = 500 objects?
